### 2016-10-18 methodsPaper/tex/results.tex
results intro

>>>>

Our subset of the US population to only metropolitan counties consisted of 1,090 of 3,141 (34.7\%) counties, or x of y (z\%) of the total US population. The age and gender distribution of our subset population was slightly younger (making this up) than the national population. Active transport times (walking and cycling) for baseline, low, and high scenarios are shown in \ref{fig:ATtimes}. Overall mean walking time for high and low scenarios were X (min/week) higher and Y (min/week) lower than baseline, respectively. Baseline non-travel activity time was estimated to be X (min/week) from the ATUS for US metropolitan populations.
